Proposed Solution

### 2016-11-14 Ennan-Proposal/intro.tex
Grammar

We propose a framework for automated verification of configuration files. 
Verifying configuration files is different than verifying standard programs: configuration
files are missing a program structure, but also a specification. They are written in a
very low level programming paradigm: they mainly consists of sequences of assignments 
of some 
values to system variables. In such framework, writing a specification is complex task, 
since it is not clear how should the specification look like and which properties should 
it address. Our framework works as follows: in the pre-processing stage, 
we first automatically derive a specification. Once we have a specification, 
we check if a given configuration 
file adheres to that specification.
Deriving a specification is based on analyzing a large number of configuration files from publicly available 
datasets. We recognize patterns and keyword correlations and from those findings we derive 
a corresponding specification. To do that we first develop a language model for configuration files. One question we 
need to address is: what if there is an error in the given training set? Our proposed framework 
is general enough that it can still derive a correct specification, under 
the assumption that the same error does not appear in a significant amount of files.
We plan to evaluate our framework on real-world configuration files 
used in the TravisIC tool.

>>>>

We propose a framework for automated verification of configuration files. 
Verifying configuration files is different than verifying standard programs: configuration
files are missing a program structure and a specification. They are written in a
very low level programming paradigm: they mainly consists of sequences of assignments 
of some 
values to system variables. In such a framework, writing a specification is a complex task, 
since it is not clear what the specification should look like and which properties should 
it address. Our framework works as follows: in the pre-processing stage, 
we first automatically derive a specification. Once we have a specification, 
we check if a given configuration 
file adheres to that specification.
Deriving a specification is based on analyzing a large number of configuration files from publicly available 
datasets. We recognize patterns and keyword correlations and from those findings we derive 
a corresponding specification. To do that we first develop a language model for configuration files. One question we 
need to address is: what if there is an error in the given training set? Our proposed framework 
is general enough that it can still derive a correct specification, under 
the assumption that the same error does not appear in a significant amount of files.
We plan to evaluate our framework on real-world configuration files 
used in the TravisIC tool.
